---
title: "12_pscyho_demogs_2"
author: "Christian Coffman"
date: "2/23/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

diags <- read.csv("~/Research/Brain_stuff/BRIDGES_GIG_ICA/Diagnoses/ALongitudinalStudyEx_DATA_LABELS_2022-02-22_1045.csv")
# grids2 <- data.frame(grid = proj2$grid, arm = proj2$redcap_event_name)
good_grids <- read.csv("/home/christian/Research/Brain_stuff/BRIDGES_GIG_ICA/switching_data.csv")$grid

```



Look at number of depressions

1. Count every subjects that has a depression diagnosis in any of the columns. I'll call these counts "Diagnosis"
2. Filter those counts by only the ones having the word "Checked" in the columns that have current in them. An example column is  "Status.of.primary.diagnosis...choice.Current." I will not count checks in other columns such as the following:
Status.of.primary.diagnosis...choice.Past
Status.of.primary.diagnosis...choice.Partial.remission.
Status.of.primary.diagnosis...choice.Full.remission
Status.of.primary.diagnosis...choice.Recurrent
Status.of.primary.diagnosis...choice.With.psychotic.features
Status.of.primary.diagnosis...choice.Missing.Skipped
Status.of.primary.diagnosis...choice.More.than.one.response
```{r}

selects <- diags %>%
  # only grab diagnosis at year 1
  filter(grepl("Year 1", Event.Name)) %>%
  # only grab subejcts for which we have scans 
  mutate(GRID.number. = as.numeric(GRID.number.)) %>%
  filter(GRID.number. %in% good_grids) %>%
  # looks like there are 124 so that's good, keep going
  dplyr::select(contains("diagnosis") | "GRID.number.") %>%
  # Exclude other designations for the diagnosis timeline
  dplyr::select(!contains("choice.Past")) %>%
  dplyr::select(!contains("choice.Partial.remission.")) %>%
  dplyr::select(!contains("choice.Full.remission")) %>%
  dplyr::select(!contains("choice.Recurrent")) %>%
  dplyr::select(!contains("choice.With.psychotic.features")) %>%
  dplyr::select(!contains("choice.Missing.Skipped")) %>%
  dplyr::select(!contains("choice.More.than.one.response")) %>%
  dplyr::select(!contains("Severity")) %>%
  dplyr::select(!contains("specify")) %>%
  dplyr::select(!contains("choice.More.than.one.response"))
```

```{r}
goods <- selects %>% 
  # pivot taller
  pivot_longer(-GRID.number., names_to = "Name", values_to = "Value")  %>% 
  # mutate s.t. the names are simpler, (i.e. there are just diagnoses and current status)
  # also add keep track of diagnosis number 
  mutate(Name = ifelse(grepl("Current", Name), "Status", "Diagnosis"), Diag = rep(rep(1:9, each=2), 124)) %>%
  pivot_wider(id_cols = c(GRID.number., Diag) ,names_from = Name, values_from = Value) %>%
  rename(grid= GRID.number.) %>%
  filter(Diagnosis != "", Diagnosis!= "No Diagnosis", Diagnosis!= "No diagnosis", !grepl("Other", Diagnosis)) %>%
  group_by(grid, Status) %>%
  # Keep all of the unique status, diagnosis identifiers
  summarize(Diagnosis = unique(Diagnosis)) %>%
  ungroup() %>%
  group_by(Status, Diagnosis) %>%
  count() %>%
  pivot_wider(names_from = Status, id_cols = Diagnosis, values_from = n) %>%
  # Calculate total number for counts of lifetime diagnoses, and calculate percentages
  mutate(Lifetime = Checked + Unchecked, Current_p = Checked/124 * 100, Lifetime_p = Lifetime/124 * 100) %>%
  rename(Current = Checked) %>%
  dplyr::select(Lifetime, Lifetime_p, Current, Current_p)


goods %>%
  filter(grepl("Post", Diagnosis))

# 86 with depression
# 68 current 

write.csv(current_depress, "/home/christian/Research/Brain_stuff/BRIDGES_GIG_ICA/current_depression.csv")

```

```{r}
# Greta broad category counts for Depression and Anxiety
selects %>% 
  # pivot taller
  pivot_longer(-GRID.number., names_to = "Name", values_to = "Value")  %>% 
  # mutate s.t. the names are simpler, (i.e. there are just diagnoses and current status)
  # also add keep track of diagnosis number 
  mutate(Name = ifelse(grepl("Current", Name), "Status", "Diagnosis"), Diag = rep(rep(1:9, each=2), 124)) %>%
  pivot_wider(id_cols = c(GRID.number., Diag) ,names_from = Name, values_from = Value) %>%
  rename(grid= GRID.number.) %>%
  filter(Diagnosis != "", Diagnosis!= "No Diagnosis", Diagnosis!= "No diagnosis", !grepl("Other", Diagnosis)) %>%
  # codify having any form of depression r anxiety
  mutate(depress = ifelse(grepl("Depress", Diagnosis), 1, 0),
         anxiety = ifelse(grepl("Anx", Diagnosis), 1, 0)) %>%
  # select fewer columns to make it easier to deal with
  dplyr::select(Status, depress, anxiety) %>%
  group_by(Status) %>%
  summarize(anxiety = sum(anxiety), depress = sum(depress)) %>%
  t() %>%
  as.data.frame() %>%
  mutate(V1 = as.numeric(V1), V2 = as.numeric(V2)) %>%
  drop_na() %>%
  rename(Current = V1, Unchecked = V2) %>%
  mutate(Lifetime = Current + Unchecked, Current_p = Current / 124 * 100, Lifetime_p = Lifetime/124 * 100) %>%
  dplyr::select(Lifetime_p, Lifetime, Current_p, Current)
```

